draft_group-6

### 2025-11-18 draft_group-6.Rmd
update

---
title: "draft_group-6"
output: pdf_document
---

@@

## motivation
(10% of the content)\
The Bank Marketing dataset contains information collected from a Portuguese banking institution during multiple direct telemarketing campaigns (source1). *Why??* (We want to justify the efforts of modeling this data)

@@

- Data wrangling/cleaning
- For each model (Logistic, LDA, QDA, KNN, Boosting )
  - Model Formulation (training data, with k-fold CV)
  - Feature Selection and model tuning (subset, regularization, dimension reduction)

@@

## references
(5%)

>>>>

---
title: "draft_group-6"
output:
  html_document:
    df_print: paged
---

@@

## motivation
(13% of the content)\
The Bank Marketing dataset contains information collected from a Portuguese banking institution during multiple direct telemarketing campaigns (source1). *Why??* (We want to justify the efforts of modeling this data)

@@

- Data wrangling/cleaning
- For each model (Logistic, LDA, QDA, KNN, GAM, Boosting)
  - Model Formulation (training data, with k-fold CV)
  - Feature Selection and model tuning (subset, regularization, dimension reduction)

@@

## references
(2%)
